\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\onehalfspacing

\title{Criterion A: Initial Investigation}
%\author{Sagindyk Urazayev}
\date{May 2017}

\begin{document}
\maketitle
%\newpage
\section*{The problem and the inadequacies of the current situation}

In my opinion, in XXI century every person with his own works and publication should have his own website with all his works as a centralized archive. That is very important to professors of various sciences and studies. My client is Bulat Mukhamediyev, professor of Al- Farabi Kazakh National University. We are contacting each other via email and the consultation was held on February 27th, 2017 via Skype. My client is a professor in a well-respected university; he is publishing his documents and scientific publications via journals, speech theses. \\

During the consultation, I have discovered, that my client has tried a new way of publishing them via email and cloud storages, but he thought it was ineffective, so we contacted. The problem is that my client couln't find a good way of sharing his publications and papers. Also, he wanted an IT System, which will have some information about him, so the visitors would have an introduction in my clien't work and life. I proposed a solution for my client's problem in the form of a personal Website.\\

As during the consultation my client told me, he will provide me with his publications in digital forms. The old ones, which do not exist in digital form and paper, only will be scanned later.\\

My client would like to have a centralized database with all his own works and publications. His students and young professors can get an easy access to his work, which would be a great source of information and data that they can rely on. From the consultation client also would like to have pages about himself and additional information that he will provide during the Implementation.\\

My client would like the website to include:

\begin{itemize}
    \item Easy to access database with his publications.
    \item Page with his biography information.
    \item Pages with good design and easy to navigate.
    \item A gallery page with my client's photos.
\end{itemize}

As to reach all points above will take a significant amount of time to prepare for the class. After the completion of the website, the website can help university students and young scientists to find the new reliable source of information and become more familiar with my client's works.\\

Word Count = 363\\

\end{document}
