\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}

\usepackage{setspace}
\title{Criterion A: Initial consultation}
\date{April 2017}
\begin{document}
\maketitle
\textbf{Date:} February 27th, 2017

\textbf{Type of interview:} Remotely via Skype – Yerevan 

\textbf{Time:} 7:30 p.m. 

\textbf{Name and position of interviewee:} Bulat Mukhamediyev, at the other end of the remote call.\\

\textit{“English translation from a Russian original”}\\

\begin{center}
    \textit{Interview starts here.}
\end{center}

\textbf{Where do you work?}\\

Al-Farabi Kazakh National University\\

\textbf{What is your job and work position?}\\

I am a professor of macro and microeconomics at Al-Farabi Kazakh National University.\\

\textbf{What is your way of publishing your scientific works and studies?}\\

Mainly in articles, scientific journals or theses at conferences. But also I would like to have another way of publishing my works.\\

\textbf{Have you tried other ways of spreading documents?}\\

Yeah, sure. I tried to make email messages and downloading documents from the cloud, but for some people, that is difficult and I also think this way of publishing is ineffective, because of the links size and I don’t have that much time to send documents via email for a long period of time. Young professors and students ask how they can get an access to my works without any third-party services and websites and I needed a service, where I can share it.\\

My previous attempts of sharing documents were unsuccessfull. The mailing option took too much time and the option with cloud services were unreliable and difficult to use.\\

I wanted a new IT system that would solve the problem of sharing my works. Also, I wanted a solution that can include some information about me, so all the visitors will have a good introduction into my sphere of work.\\

\textbf{As an effective solution, I think you would like to have your own website, which will contain a full-centralized database of all your scientific works and studies and this website can be your business card.}\\

Yes, I would like to, that is a good idea. I think it would be great to have a website with all my publications in one place because young scientists and other professors could read my works and find out something new. I think it would be very effective and easy to use in the future. I have been writing scientific works for almost 45 years. I can provide the website with all materials needs, including my papers. Unfortunately, some of my old publications exist only in hardcopy, so no digital version exists. However, if needed, I can scan them and later send them. \\

And also, I think it would be good if biography page will be included. \\

And of course, the website should look good and easy to navigate, so I would like to have a gallery page, where my photos can be published.\\

\textbf{So, you want to have a centralized database of your works?}\\

That is correct.\\

\textbf{How often would you like the site to be updated?}\\

Minimum once a year to add new studies and add some information if needed.\\

\textbf{Will you like to update the website by yourself or use someone’s help?}\\

I am not sure quite enough how to do it, but I’m sure I will learn how to.\\

\begin{center}
    \textit{Interview ends here.}
\end{center}

\end{document}
